---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gecm

<!-- badges: start -->
<!-- badges: end -->

The `gecm` package contains functions for the analysis of change within raster time-series data. The following methods are (or will be) implemented:

1. Harmonic Regression/Seasonal Trends Analysis: Change detection through analysis of reoccurring signals.
2. Prophet: Detection of spatially and/or temporally contiguous groups of anomalies

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dahcase/gecm")
```
## Example (Harmonic Regression)

```{r example}
library(gecm)
library(terra)

#Load a simple raster time series
ouaga = system.file('extdata/ouaga_dates.tif', package = 'gecm')
ouaga = rast(ouaga)

#plot a few layers
plot(subset(ouaga, c(1, 100, 200, 300)))

#plot the time series of a pixel
px1 = ouaga[1]
plot(unlist(px1), type = 'l')

#run the harmonic regression
res = harmonic(r = ouaga, 
               harmonic_value = 2, # num harmonics
               'all', #values to return
               window = 23 #determines window size.
                           #For this product, find the seasonality per year
               ) 

#plot the results for A1 for all windows. Where A1 is the peak seasonality.
A1s = grep('A1', names(res))

plot(subset(res, A1s))


```

## Example (Prophet)

```{r}
library('gecm')
library('terra')
# Load data
ouaga = system.file('extdata/ouaga_dates.tif', package = 'gecm')
ouaga = rast(ouaga)

# compute yhats
pouaga = prophet_rast(ouaga, as.Date(names(ouaga), '%Y_%m_%d'))

# compute anomalies
aouaga = find_anomaly(pouaga, ouaga, thresh = 1.65, groups = c('space', 'time', 'combined'))


```


